---
title: "Working with the Carl Nielsen Works Data"
format: html
editor: visual
---

# Loading Libraries

```{r}
library(tidyverse)
library(tidytext)
```

# Load data

```{r}
cnw <- readRDS("../data-output/cnw_dataframe.rds")
```

# Which authors has Carl Nielsen composed most music to:

```{r}
cnw %>% 
  filter(author != "") %>% 
  count(author, sort = TRUE)
```

# Which city/place has seen most performances of Carl Nielsen Works?

For now we'll just look at a single work:

```{r}
cnw %>% 
  filter(title_da == "Saul og David")
```

We see that the row under performances holds a "tibble", which is a dataframe. This dataframe contains all the performances of Saul and David, but we cant count how many because it is in a dataframe within a row. But we can unpack this dataframe while retaining all the other information:

```{r}
cnw %>% 
  filter(title_da == "Saul og David") %>% 
  unnest(performances)
```

There is 112 performances of Saul and David. But this is just for one work. We do the same for the entire dataset and save it to a new data frame, since we are changing dramatically on the form of of the data. We're making the shift from having one work pr. row to have one performances of a work pr. row:

```{r}
cnw_performances <- cnw %>%
  unnest(performances) 
```

Since all the other data have been retained for each performances we can now count to see which work has been performened the most:

```{r}
cnw_performances %>% 
  count(title_da, sort = TRUE)
```

Following the same logic we can also examine which city has seen the most performances:

```{r}
cnw_performances %>% 
  count(place, sort = TRUE)
```

Copenhagen is out of proportions - lets filter it out for a nice visualisation:

```{r}
cnw_performances %>% 
  filter(place != "") %>% 
  filter(place != "Copenhagen") %>% 
  count(place, sort = TRUE) %>% 
   slice_max(n, n = 15) %>% 
  mutate(place = reorder(place, n)) %>%
  ggplot(aes(x = place, y = n)) +
  geom_col(fill = "lightblue") +
  coord_flip() +
  labs(
    title    = "Performances of Carl Nielsen works outside of Copenhagen",
    subtitle = "- dispersed on cities",
    caption = "Data from Catalogue of Carl Nielsen's Works (CNW)",
    x = "City",
    y = "Count of performances"
  ) 
```
```{r}
ggsave("../graphics/cnw_performances_outside_cph.png", width = 20, height = 14, units = "cm")
```

# Which titles in which countries?

Load geographical data about cities with 3 or more performances of Carl Nielsen Works:

```{r}
cnw_cities <- readRDS("../data-output/20241020_cnw_performances_geographical_information.rds")
```

Add the geographical data to the performances data frame:

```{r}
cnw_performances <- cnw_performances %>% 
  left_join(cnw_cities, by = "place")
```

Dispersions of performances on country:

```{r}
cnw_performances %>% 
  drop_na(country) %>% 
  count(country, sort  = TRUE)
```

Which titles has been performed the most in Denmark:

```{r}
cnw_performances %>% 
  filter(country == "Danmark") %>% 
  count(title_da, sort = TRUE)
```
